Approximation as Differentiation

### 2025-06-02 main/higher-order.tex
Moving from Set semantics to arbitrary C..

\input{fig/mu-polynomial}
\input{fig/set-semantics}

@@

\figref{set-semantics:types} gives the interpretation of a type $\tau$ with a single free type variable as an
endofunctor on $\Set$.

>>>>

\input{fig/mu-polynomial}
\input{fig/default-semantics}

@@

Suppose $\cat{C}$ a Cartesian closed category with finite coproducts, a strong monad $\mathcal{L}$ and
$\mu$-polynomial endofunctors given by $\muPoly_{\cat{C}}$. \figref{default-semantics:types} gives the
interpretation of a type $\tau$ with a single free type variable as a $\mu$-polynomial endofunctor on
$\cat{C}$.
